\documentclass[a4paper,man,natbib]{apa6}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

% Uncomment only one of the ones below
\usepackage{anonymize} % uncomment to publish
%\usepackage[blind]{anonymize} % uncomment to for blind review

\title{Using the anonymize package}
\shorttitle{Using the anonymize package}
\author{\anonymize{Angelo Fraietta}}
\affiliation{\anonymize{University of New South Wales}}

\abstract{One of the things I find particularly frustrating with blind reviewed papers was finding substitute text that did not detract from the flow of thought. This is the case in both writing and the reviewing the manuscript. Moreover, reverting changes for publication  once the paper has been reviewed is not only time consuming, but very susceptible to errors. Furthermore, having to modify references that could identify me or my co-authors and then swapping from review to publish mode was also inconvenient.

This document details a new package that facilitates generating manuscripts that require you to mask parts of the document that could identify you as the author.}

\begin{document}
\maketitle

\section{Introduction}
Many conferences and journals require authors to submit their manuscripts so that the author's identity is concealed from the reviewer. One of the things I find particularly frustrating with blind reviewed papers was finding substitute text that did not detract from the flow of thought. This is the case in both writing and the reviewing the manuscript. Moreover, reverting changes for publication  once the paper has been reviewed is not only time consuming, but very susceptible to errors. Furthermore, having to modify references that could identify me or my co-authors and then swapping from review to publish mode was also inconvenient.

This example showing how to use the \textit{anonymize} package. 

Questions may be directed to a.fraietta@unsw.edu.au. Please put [Blind Latex] in the subject line.

%use of references
\section{Use of the package}
A convenient flag has been provided that will allow you to easily mask any text or reference that could be used to identify you as the author. To enable the feature, comment the line \texttt{\textbackslash usepackage{anonymize} } and uncomment the \texttt{\textbackslash usepackage[blind]{anonymize} } lines near the top of the file. When \texttt{\textbackslash usepackage[blind]{anonymize} } is enabled, anonymized text will be blackened out and masked bibliography names and titles will be anonymised. For example, the following will cause the package to generate a blind review version of the manuscript.\\

\texttt{\% \textbackslash usepackage{anonymize} uncomment to publish} \\
\texttt{\textbackslash usepackage[blind]{anonymize} \% uncomment to for blind review} \\

	
The following configuration will cause the manuscript to disable masking text and produce the version of the manuscript for publication.

\texttt{\textbackslash usepackage{anonymize} uncomment to publish} \\
\texttt{\%\textbackslash usepackage[blind]{anonymize} \% uncomment to for blind review} \\

\subsection{Masking text}
To mask text that may identify you, place the text you want to hide inside the \textbackslash anonymize function. If you have enabled the blind review feature, \anonymize{you will Change back to the non-blind mode when you are ready to publish}. 


\subsection{References}
LaTeX automatically generates a bibliography in the APA style from your .bib file. The citep command generates a formatted citation in parentheses \citep{Lamport1986}. The cite command generates one without parentheses. LaTeX was first discovered by \cite{Lamport1986}.

\subsubsection{Masking publications}
In order to mask your publications,  you will need to make a copy of your personal references, using the second version with a key name adding \texttt{-hidden}. For example, if your reference key is \texttt{myotherpublication}, make a copy called \texttt{myotherpublication-hidden} that has text displayed how you would like it displayed in blind review mode.  Wrap your reference name with the \textit{anoncite} function. For example, to make \texttt{{\char'134}cite\{mypublication\}} anonymous in the blind version, use the following instead.
\texttt{{\char'134}cite\{{\char'134}anoncite\{mypublication\}\}}.
You will note that \cite{\anoncite{mypublication}} and \cite{\anoncite{myotherpublication}} were written by me, so in blind mode, the identifying parts will be suppressed.

Some examples for the use of references in the text:\\

\cite{Lamport1986}, \cite{\anoncite{mypublication}} 

%reference in brackets, multiple authors
\citep*{Lamport1986}, \citep*{\anoncite{myotherpublication}}  

\section{Original Source}
This template was based on the APA6 packagae obtained through Overleaf and was covered under the Creative Commons CC BY 4.0
Commons CC BY 4.0 \cite{overleafAPA6Reference}.
The code for creating the black boxes was originally found at \cite{texStackExchange}
I hope you find this package useful. Also, please excuse the non-Australian spelling of \textit{anonymize}.

\bibliography{example}

\end{document}

%
% Please see the package documentation for more information
% on the APA6 document class:
%
% http://www.ctan.org/pkg/apa6
%